### 2022-02-23 sections/systematic_uncertainties.tex
updates for more comments

Several normalisation and shape uncertainties are taken into account for the $\Hq$ and $pp\to tH$ signals.
Uncertainties of the Higgs boson branching ratios are taken into account
following the recommendation in Ref.~\cite{deFlorian:2016spz}.
The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties are estimated by comparing
the nominal to an alternative sample interfaced with {\herwig7}.
%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
%treated correlatedly with $\ttbar$ samples.

\begin{table}[h!]
\caption{List of relative uncertainties on the upper limits of $\BR(t\to qH)$ ($q=u,c$) obtained from the combined fit. The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
\label{tab:had_sys_impact}
\begin{center}
\begin{tabular}{%
@{}l%
S%
S%
@{}%
}
\toprule\toprule
\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\BR/\BR [\%]$} \\
                                            & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
%Lepton                                  & 0.6           &1.0         \\
%Met                                     & 0.7           &0.8         \\
%Luminosity and Pileup                   & 1.0           &1.3         \\
%Theoretical uncertainty in other MC     & 2.1           &2.9         \\
%Jets                                    & 2.4           &3.2         \\
%Flavour tagging                         & 2.7           &3.7         \\
%Misidentified $\tau$                    & 3.4           &4.8         \\
%Theoretical uncertainty in $t\bar{t}$   & 2.9           &4.3         \\
%Hadronic $\tau$ decays                  & 3.3           &4.4         \\
%Theoretical uncertainty in signal       & 5.3           &7.0         \\\midrule
%Total statistics uncertainty            & 5.1           &7.0         \\
%Total systematic uncertainty            & 11.2          &15.4        \\ \midrule
%Total                                   & 12.3          &16.9        \\

Lepton ID                               & 0.6           &1.0         \\
Met                                     & 0.7           &0.8         \\
Fake lepton  modeling                   & 0.9           &1.1         \\
Luminosity and Pileup                   & 0.9           &1.3         \\
Other MC modeling                       & 2.1           &2.9         \\
JES and JER                             & 2.4           &3.2         \\
Flavour tagging                         & 2.7           &3.7         \\
$t\bar{t}$ modeling                     & 2.9           &4.3         \\
Fake $\tau$ modeling                    & 3.2           &4.6         \\
$\tau$ ID                               & 3.3           &4.4         \\
Signal modeling including Br($H\to\tau\tau$)       & 5.3           &7.0         \\\midrule
Total systematic uncertainty            & 11.2          &15.5        \\ 
Total statistics uncertainty            & 5.1           &7.0         \\\midrule
Total                                   & 12.3          &17.0        \\

@@

\bottomrule\bottomrule
\end{tabular} 
\end{center}
\end{table}

>>>>

Several normalisation and shape uncertainties are taken into account for the $\Hq$ and $pp\to tH$ signals.
Uncertainties of the Higgs boson branching ratios are taken from the measured values in Ref.~\cite{Zyla:2020zbs}.
%into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties are estimated by comparing
the nominal to an alternative sample interfaced with {\herwig7}.
%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
%treated correlatedly with $\ttbar$ samples.

%\begin{table}[h!]
%\caption{List of relative uncertainties on the upper limits of $\BR(t\to qH)$ ($q=u,c$) obtained from the combined fit. The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
%\label{tab:had_sys_impact}
%\begin{center}
%\begin{tabular}{%
%@{}l%
%S%
%S%
%@{}%
%}
%\toprule\toprule
%\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\BR/\BR [\%]$} \\
%                                            & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
%Lepton                                  & 0.6           &1.0         \\
%Met                                     & 0.7           &0.8         \\
%Luminosity and Pileup                   & 1.0           &1.3         \\
%Theoretical uncertainty in other MC     & 2.1           &2.9         \\
%Jets                                    & 2.4           &3.2         \\
%Flavour tagging                         & 2.7           &3.7         \\
%Misidentified $\tau$                    & 3.4           &4.8         \\
%Theoretical uncertainty in $t\bar{t}$   & 2.9           &4.3         \\
%Hadronic $\tau$ decays                  & 3.3           &4.4         \\
%Theoretical uncertainty in signal       & 5.3           &7.0         \\\midrule
%Total statistics uncertainty            & 5.1           &7.0         \\
%Total systematic uncertainty            & 11.2          &15.4        \\ \midrule
%Total                                   & 12.3          &16.9        \\

%Lepton ID                               & 0.6           &1.0         \\
%$\met$                                  & 0.7           &0.8         \\
%Fake lepton  modeling                   & 0.9           &1.1         \\
%Luminosity and Pileup                   & 0.9           &1.3         \\
%Other MC modeling                       & 2.1           &2.9         \\
%JES and JER                             & 2.4           &3.2         \\
%Flavour tagging                         & 2.7           &3.7         \\
%$t\bar{t}$ modeling                     & 2.9           &4.3         \\
%Fake $\tau$ modeling                    & 3.2           &4.6         \\
%$\tau$ ID                               & 3.3           &4.4         \\
%Signal modeling including Br($H\to\tau\tau$)       & 5.3           &7.0         \\\midrule
%Total systematic uncertainty            & 11.2          &15.5        \\ 
%Total statistics uncertainty            & 5.1           &7.0         \\\midrule
%Total                                   & 12.3          &17.0        \\

@@

%\bottomrule\bottomrule
%\end{tabular} 
%\end{center}
%\end{table}
